Adaptation of Palmer amaranth to the upper Midwest

### 2021-07-05 Frontiers/Frontiers.Rmd
as

---
title: "Adaptation of Palmer amaranth to the upper Midwest"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Maxwel C Oliveira
    affiliation: '1'
    etal: Oliveira # First author's last name. 
  - name: Amit J Jhala
    affiliation: '2'
  - name: Mark Bernards
    affiliation: '3'
  - name: Chris Proctor
    affiliation: '2'
  - name: Strahinja Stepanovic
    affiliation: '2'
  - name: Rodrigo Werle
    affiliation: '1'
    email: rwerle@uwisc.edu # Indicates corresponding Author
    institution: Department of Agronomy, University of Wisconsin-Madison, United States
    street: 1575 Linden Dr
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    zip: 53705
    country: United States
affiliation:
  - id: '1'
    department: Department of Agronomy
    institution: University of Wisconsin-Madison
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    country: United States
  - id: '2' 
    department: Department of Agronomy and Horticulture
    institution: University of Nebraska-Lincoln
    city: Lincoln
    state: Nebraska # only USA, Australia, Canada
    country: United States
  - id: '3' 
    department: Department of Agronomy
    institution: Western Illinois University
    city: Macomb
    state: Illnois # only USA, Australia, Canada
    country: United States
output: rticles::frontiers_article
csl: frontiers.csl
bibliography: test.bib
---

@@

# Introduction {-}
Cite fancy references [@Neuro2013]. As demonstrated in @Gene2012, citations can
also be automatically reference. Multiple references are separated by semicolons
[@Neuro2013; @Neurobot2013].

@@

## Plant material {-}

The study was performed with a *A. palmeri* accession (Per1) from Perkins County, Nebraska. Per1 accession collection is documented in [], with no  confirmed herbicide resistance.

>>>>

---
title: "Adaptation of Palmer amaranth to the upper Midwest"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: Maxwel C Oliveira
    affiliation: '1'
    etal: Oliveira # First author's last name. 
  - name: Amit J Jhala
    affiliation: '2'
  - name: Mark Bernards
    affiliation: '3'
  - name: Chris Proctor
    affiliation: '2'
  - name: Strahinja Stepanovic
    affiliation: '2'
  - name: Rodrigo Werle
    affiliation: '1'
    email: rwerle@uwisc.edu # Indicates corresponding Author
    institution: Department of Agronomy, University of Wisconsin-Madison, United States
    street: 1575 Linden Dr
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    zip: 53705
    country: United States
affiliation:
  - id: '1'
    department: Department of Agronomy
    institution: University of Wisconsin-Madison
    city: Madison
    state: Wisconsin # only USA, Australia, Canada
    country: United States
  - id: '2' 
    department: Department of Agronomy and Horticulture
    institution: University of Nebraska-Lincoln
    city: Lincoln
    state: Nebraska # only USA, Australia, Canada
    country: United States
  - id: '3' 
    department: Department of Agronomy
    institution: Western Illinois University
    city: Macomb
    state: Illnois # only USA, Australia, Canada
    country: United States
output: rticles::frontiers_article
csl: frontiers.csl
bibliography: adaptation.bib
---

@@

# Introduction {-}

Cite fancy references [@Neuro2013]. As demonstrated in @Gene2012, citations can
also be automatically reference. Multiple references are separated by semicolons
[@Neuro2013; @Neurobot2013].

@@

## Plant material and growing conditions {-}

The study was performed with a *A. palmeri* accession (Per1) from Perkins County, Nebraska. Per1 accession collection is documented in [@oliveira2021a], with no reported herbicide resistance. Seeds were planted in plastic trays containing potting-mix. Emerged seedlings (1 cm) were transplanted into 200 cm<sup>-3</sup> plastic pots (a plant pot<sup>-1</sup>). Palmer amaranth seedlings were supplied with adequate water and kept under greenhouse conditions at Arlington, Clay Center, Lincoln, and Macomb; and kept outdoors in Grant. At 7 to 10 cm height, Palmer amaranth seedlings were transplanted to the field for the onset of the experiment.

## Field study {-}

The experiment was conducted under field conditions at five locations: Arlington, WI (Washington County), Clay Center, NE (Clay County), Grant, NE (Perkins County), Lincoln, NE (Lancaster County), and Macomb, IL (McDonough County)

### 2021-07-05 Frontiers/Frontiers.tex
as

Cite fancy references (LastName1 et al., 2013). As demonstrated in
OtherAuthor and Coauthor (2012), citations can also be automatically
reference. Multiple references are separated by semicolons (LastName1 et
al., 2013; Author4 and Author5, 2013).

@@

The study was performed with a \emph{A. palmeri} accession (Per1) from
Perkins County, Nebraska. The accession Per1 was documented as
glyphosate-susceptible {[}{]}.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Neurobot2013}{}%
Author4, N., and Author5, N. (2013). Title of the article.
\emph{Frontiers in Neurorobotics} 7.
doi:\href{https://doi.org/10.3389/fnbot.2013.56789}{10.3389/fnbot.2013.56789}.

\leavevmode\hypertarget{ref-Neuro2013}{}%
LastName1, A., LastName2, A., and LastName2, A. (2013). Article title.
\emph{Frontiers in Neuroscience} 30, 10127--10134.
doi:\href{https://doi.org/10.3389/fnins.2013.12345}{10.3389/fnins.2013.12345}.

\leavevmode\hypertarget{ref-Gene2012}{}%
OtherAuthor, N., and Coauthor, N. S. (2012). Article title.
\emph{Frontiers in Genetics} 30, 16417--16418.
doi:\href{https://doi.org/10.3389/fgene.2012.54321}{10.3389/fgene.2012.54321}.

>>>>

Cite fancy references (\textbf{Neuro2013?}). As demonstrated in
(\textbf{Gene2012?}), citations can also be automatically reference.
Multiple references are separated by semicolons (\textbf{Neuro2013?};
\textbf{Neurobot2013?}).

@@

The study was performed with a \emph{A. palmeri} accession (Per1) from
Perkins County, Nebraska. Per1 accession collection is documented in
(Oliveira et al., 2021), with no reported herbicide resistance. Seeds
were planted in plastic trays containing potting-mix. Emerged seedlings
(1 cm) were transplated into 200 cm-3 plastic pots. Palmer amaranth
seedlings supplied with adequate water and kept under greenhouse
conditions at 28/20 C day/night temperature with 80\$ relative humidity.
Artificial lighting was provided using metal halide lamps (600 mmol m-2
s-1) to ensure 15-h photoperiod.

The experiment was conducted under field conditions at five locations:
Arlington, WI (Washington County), Clay Center, NE (Clay County), Grant,
NE (Perkins County), Lincoln, NE (Lancaster County), and Macomb, IL
(McDonough County)

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-oliveira2021a}{}%
Oliveira, M. C., Giacomini, D. A., Arsenijevic, N., Vieira, G., Tranel,
P. J., and Werle, R. (2021). Distribution and validation of genotypic
and phenotypic glyphosate and {PPO}-inhibitor resistance in {Palmer}
amaranth ({Amaranthus} palmeri) from southwestern {Nebraska}. \emph{Weed
Technology} 35, 65--76.
doi:\href{https://doi.org/10.1017/wet.2020.74}{10.1017/wet.2020.74}.
